The first high-redshift Changing Look Quasars

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191030.tex
CIV tex/ tidy up

\author[Bercow]
{The RH John~S.~Bercow, MP, {\it et al.} 
%Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},    
%K. E. Saavik Ford$^{2,3,4}$,  Matthew Graham$^{5}$,  Barry McKernan$^{2,3,4}$,  
%\newauthor Daniel Stern$^{6}$, 
\\
% List of institutions
$^{1}$Speaker's Chair, The House of Commons, London, SW1A 0AA \\
%$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
%$^{2}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
%$^{3}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
%$^{4}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
%$^{5}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
%$^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
}

@@

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/Wilhite_2006_Fig2_redux_20190926.png}
   \vspace{-12pt}
  \caption[]{The Change in \civ\ line width vs. line flux change. 
We compare our object J1638+2827 with the sample 
from \citet{Wilhite2006} with a sample of 105 quasars observed at
multiple epochs by the SDSS. J1638+2827 is a substantial outlier 
in this parameter space.}
  \label{fig:Wilhite2006_comparison}
\end{figure}
\subsection{Overall Spectral Evolution}
Emission line measurements from the catalogues of  \citet{Shen2011}.
\citet{Hamann2017}, \citet{Kozłowski2017} or the QSFit routine of \citet{Calderone2017}
are presented in Table~\ref{tab:LineMeasurement}.
%%
From Figure~\ref{fig:Wilhite2006_comparison} there appears to be a
strong correlation between the change in the line flux and the change
in the line width.  Figure~\ref{fig:Wilhite2006_comparison} shows the
epoch-to-epoch flux ratio versus the ratio of line widths.

@@

>>>>

\author[Bercow]
{The RH John~S.~Bercow, MP, {\it et al.} 
  % Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},
  %Matthew Graham$^{2}$, K. E. Saavik Ford$^{3,4,5}$,    Barry McKernan$^{3,4,5}$,  
%\newauthor Daniel Stern$^{6}$, 
\\
% List of institutions
$^{1}$Speaker's Chair, The House of Commons, London, SW1A 0AA \\
%$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
%$^{2}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
%$^{3}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
%$^{4}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
%$^{5}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
%$^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
}

@@

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/Wilhite_2006_Fig2_redux_20190926.png}
   \vspace{-12pt}
  \caption[]{The Change in \civ\ line width vs. line flux change. 
We compare our object J1638+2827 with the sample 
from \citet{Wilhite2006} with a sample of 105 quasars observed at
multiple epochs by the SDSS. J1638+2827 is a substantial outlier 
in this parameter space.}
  \label{fig:Wilhite2006_comparison}
\end{figure}
\subsection{Overall Spectral Evolution}
Emission line measurements from the catalogues of  \citet{Shen2011}.
\citet{Hamann2017}, \citet{Kozlowski2017} or the QSFit routine of \citet{Calderone2017}
are presented in Table~\ref{tab:LineMeasurement}.
%%
From Figure~\ref{fig:Wilhite2006_comparison} there appears to be a
strong correlation between the change in the line flux and the change
in the line width.  Figure~\ref{fig:Wilhite2006_comparison} shows the
epoch-to-epoch flux ratio versus the ratio of line widths.

@@

The X-ray Baldwin Effect \citet[e.g., ][]{Iwasawa_Taniguchi1993}
\citet{Bachev2004} find a 10-fold decrease in EW C IV λ1549 with
Eddington ratio (decreasing from ~1 to ~0.01), while N V λ1240 shows
no change. These trends suggest a luminosity-independent ``Baldwin
effect'' in which the physical driver may be the Eddington ratio.
\citet{Ge2016} Broad emission lines is a prominent property of type I quasi-stellar objects (QSOs).

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191031.tex
CIV tex/ tidy up

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/Wilhite_2006_Fig2_redux_20190926.png}
   \vspace{-12pt}
  \caption[]{The Change in \civ\ line width vs. line flux change. 
We compare our object J1638+2827 with the sample 
from \citet{Wilhite2006} with a sample of 105 quasars observed at
multiple epochs by the SDSS. J1638+2827 is a substantial outlier 
in this parameter space.}
  \label{fig:Wilhite2006_comparison}
\end{figure}
\subsection{Emission line evolution}
Emission line measurements from the catalogues of  \citet{Shen2011}.
\citet{Hamann2017}, \citet{Kozlowski2017} or the QSFit routine of \citet{Calderone2017}
are presented in Table~\ref{tab:LineMeasurement}.
%%
From Figure~\ref{fig:Wilhite2006_comparison} there appears to be a
strong correlation between the change in the line flux and the change
in the line width.  Figure~\ref{fig:Wilhite2006_comparison} shows the
epoch-to-epoch flux ratio versus the ratio of line widths.

@@

  \begin{tabu}{l ll  ll cc c r }

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

\begin{table}
  \begin{centering}
    \begin{tabular}{c c l l}
      \hline
      \hline
      Object             & MJD      & Cont. Lumin        &  Cont. slope \\
      \hline
                             & 53498   &  40040$\pm$34  & -1.656$\pm$ 0.006 \\
      J1205+3422    & 58538   &   ---                   &  ---     \\
                             & 58693   &   ---                    &  ---     \\
                             &              &                             & \\
                             & 54553   &  3774$\pm$111   &  -1.472$\pm$0.197   \\
      J1638+2827    & 55832  &  2433$\pm$14     &  -2.316$\pm$0.051  \\  
                             & 58583   &  3292$\pm$9       &    -0.541$\pm$0.010 \\
                             &              &                             &\\
                            & 56189    &  ---                      &  ---     \\
    J2228+2201     & 56960   &  7889$\pm$14      &  -1.729$\pm$0.015     \\
                            & 58693   &  ---                       &  ---     \\
    \hline
    \hline
  \end{tabular}
  \caption{Quasar continuum $\nu L_{\nu}$ luminosities and slopes, at
the fixed rest-frame wavelengths 1450\AA\ from QSFIT.  The
luminosities are in units of 10$^{42}$~erg~s$^{-1}$.}
  \label{tab:Baldwin}
  \end{centering}
\end{table}

@@

\subsection{The \civ\ Baldwin Effect}
The Baldwin Effect (Baldwin 1977) is an empirical %inverse
relation between emission-line REWs and continuum luminosity in
quasars \citep[][]{Shields2007, Hamann2017, Calderone2017}
%%
There is an anti-correlation between the emission-line REWs and e.g. 1450\AA\ rest continuum luminosity,
so that as the underlying UV continuum luminosity increases, the EW decreses,
see Figure~\ref{fig:CIV_Baldwin}
The slope $\beta$ is $-0.1997$. 
Checking with \citet{Kozlowski2017}, using their bolometric luminosity gives a slope of $\beta=-0.251$,
in line with that from \citet{Hamann2017} ($\beta=-0.23$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_REWvsFWHM_20191029.png}
   \vspace{-12pt}
  \caption[]{The Rest Equivalent Width (REW) vs. Full Width Half Maximum (FWHM) 
of the \civ\ emission line in the BOSS DR12 quasar sample using the catalogue 
of \citet{Hamann2017}. %Note the REW logarithmic scaling.
}
  \label{fig:REWvsFWHM}
\end{figure}

@@

\subsection{The Baldwin Effect}
The variable properties of the rest-frame UV quasar emission lines
have been long studied, with the global (or ensemble) Baldwin Effect
(the anti-correlation between the EW of the emission line and the
underlying continuum luminosity of single-epoch observations of a
large number of AGN, first noted in \citet{Baldwin1977}.  More
recently, the intrinsic Baldwin effect, the same anti-correlation but
in an individual, variable AGN.  The variable properties of high-$z$
quasars, however, has been less well studied. Reasons for this include
more massive systems will tend to have longer timescales with e.g.
$t_{\rm dyn}  \sim M^{2}$ if $t_{\rm dyn} = \sqrt{ R^{3}/GM}$ and $R_{\rm Sch}= 2GM /c^{2}$.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_Baldwin_20191104v3.png}
   \vspace{-12pt}
   \caption[]{The \civ\ Equivalent width and the underlying continuum luminosity,
     commonly referred to as The Baldwin Plot. The continuum luminosities are
     from \citet{Kozlowski2017},
     the REW measurements are Table~\ref{tab:Baldwin}.}
  \label{fig:CIV_Baldwin}
\end{figure}

\subsection{Variability around billion solar mass black holes} 
The Event Horizon Telescope (EHT) mapped the central compact radio
source of the elliptical galaxy M87 at 1.3 mm \citep{EHT2019_PaperI, EHT2019_PaperII, EHT2019_PaperIII, EHT2019_PaperIV, EHT2019_PaperV, EHT2019_PaperVI} .

The EHT observsations confirm the observed 1.3mm asymmetric ring
emission is consistent with predictions of strong
gravitational lensing of synchrotron emission from a hot plasma
orbiting near the black hole event horizon \citep{EHT2019_PaperV}.

EHT2017 data includes tracks from four separate
days of observing,;each day is 2.8$r_{g}$ $c^{-1}$ \citep{EHT2019_PaperIV} timescale is short
compared to the decorrelation timescale of simulated images, which is
$\sim$50 $r_{g}$ $c^{-1}$, and smaller than the light-crossing time of the source
plasma.

From \citet{EHT2019_PaperI}, $M_{M87^{*}} = (6.5\pm0.7) \; \times \; 10^{9}$ $M_{\odot}$, 
\begin{equation}
R_{s} = 2 r_{g} =  2 GM/c^{2}  = 9.598 \times10^{12} {\rm m}.
\end{equation}
giving a {\it light crossing timescale} of $t_{\rm lt} = R_{s} / c = 32 015 {\rm secs}$ (0.37 days).
%\begin{equation}
%t_{\rm lt} = R_{s} / c = 32015 {\rm secs}$
%\end{equation}
%and a {\it dynamical timescale}, $t_{\rm dyn}$
%\begin{equation}
%$t_{\rm dyn}  =  sqrt{ R_{s}^{3}/G M}
% \end{equation}
%also (!!!!!) of $t_{\rm dyn}  =  \sqrt{ R_{s}^{3}/G M}$ = 32015 seconds.

$\log_{10} (M_{M87^{*}} / M_{\odot} ) = 9.813$. 
which is only about double that of J1205+3422 and J2228+2201,
and a factor of $\sim$6 that of J1638+2827.
However, M87

@@

\noindent
We thank:
\begin{list}{$\circ$}{}
  \item  Dr. Giorgio Calderone for discussions to the utility of the QSFit routine and line measurements. 
  \item Andy Lawrence, Mike Hawkins and David Homan for useful discussion.
\end{list}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/Wilhite_2006_Fig2_redux_20190926.png}
   \vspace{-12pt}
  \caption[]{The Change in \civ\ line width vs. line flux change. 
We compare our object J1638+2827 with the sample 
from \citet{Wilhite2006} with a sample of 105 quasars observed at
multiple epochs by the SDSS. J1638+2827 is a substantial outlier 
in this parameter space.}
  \label{fig:Wilhite2006_comparison}
\end{figure}
\subsection{Overall Spectral Evolution}
Emission line measurements from the catalogues of  \citet{Shen2011}.
\citet{Hamann2017}, \citet{Kozlowski2017} or the QSFit routine of \citet{Calderone2017}
are presented in Table~\ref{tab:LineMeasurement}.
%%
From Figure~\ref{fig:Wilhite2006_comparison} there appears to be a
strong correlation between the change in the line flux and the change
in the line width.  Figure~\ref{fig:Wilhite2006_comparison} shows the
epoch-to-epoch flux ratio versus the ratio of line widths.

@@

  \begin{tabu}{l ll  lccc c r }

@@

                                            %& 58538     & \lya      & 1393$\pm$11   & $>$15000            &  $-796\pm57$          &  ---                        &  ---                       &   QSFit  \\    %% (NPR) 

@@

    \rowfont{\color{blue}}      %& 58538     & \civ      &       0$\pm$-    & 14995$\pm$0       & $>$3000$\pm$         &  ---                       &  ---                       &   QSFit  \\   %% (MJG)
%                                            & 58538      & \ciii     &  677$\pm$4     & $>$15000             & $>$3000                    &  5770$\pm$34       &  ---                       &  QSFit  \\    %% (NPR) 

@@

%    \rowfont{\color{teal}}      & 58538     & \mgii    &  755$\pm$4     & $>$15000            & 350$\pm$39               &  7571$\pm$37       &  ---                       &  QSFit  \\    %% (NPR) 

@@

%                                           & 58693     & \lya     &  290$\pm$3       & 8803$\pm$52     &  $-1096\pm35$        &  ---                           & $<$-3                   &   QSFit \\    %% (NPR) 

@@

%    \rowfont{\color{blue}}    & 58693     & \civ      &   68$\pm$0.9    & 3743$\pm$26     &   591$\pm$17           &   ---                           & $<$-3                   &  QSFit  \\    %% (NPR) 

@@

%                                           & 58693     & \ciii     &   19$\pm$0.4    & 5625$\pm$          &   $>$3000                 &  988$\pm$20             & $<$-3                   &  QSFit  \\    %% (NPR) 

@@

%   \rowfont{\color{teal}}      & 58693     & \mgii    &  19$\pm$0.4    & 1530$\pm$22      &  $>$3000                  &    499$\pm$9             &$<$-3                    &  QSFit  \\     %% (NPR) 

@@

%                                               & 58583       & \lya    &  1086$\pm$14  & $>$15000     	&   $-1047\pm88$        &  500$\pm$6   	  & $-0.443\pm0.01$    &   QSFit  \\ %% (NPR) 

@@

%   \rowfont{\color{blue}}         & 58583      & \civ      &  659$\pm$5     & $>$15000                &  $-493\pm56$          &   333$\pm$3           & $-0.43\pm0.01$     &   QSFit   \\%% (NPR) 

@@

%                                               & 58583      & \ciii      &  239$\pm$4    &  $>$15000               &  1514$\pm$127        &  124$\pm$2            & $-0.43\pm0.01$     &   QSFit  \\   %% (NPR) 

@@

%   \rowfont{\color{teal}}           & 58583      & \mgii   &  129$\pm$3    &  10957$\pm$307    &  138$\pm$128          &   78$\pm$2              & $-0.43\pm0.01$     &   QSFit   \\%% (NPR) 

@@

%                                               & 58693     & \lya      &  228$\pm$3       & 4279$\pm$32       &   $-1000\pm29$     &  91976$\pm$1311  &  ---                       &  QSFit (NPR)\\   %% (NPR) 

@@

%     \rowfont{\color{blue}}        & 58693     & \civ      &  327$\pm$1      &  $>$15000             &   $-453\pm34$       &  20298$\pm$106    & ---                        &  QSFit (NPR)\\  %% (NPR) 

@@

%                                               & 58693     & \ciii      & 269$\pm$1.5    &  $>$15000             &  2302$\pm$42.6     &   3776$\pm$21      & ---                          &  QSFit (NPR) \\  %% (NPR) 

@@

%     \rowfont{\color{teal}}        & 58693     & \mgii    &  89$\pm$1.4     &  $>$15000             &  $>$1000                &   1230$\pm$1.9    & ---                            &   QSFit  \\  %% (NPR) 

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/CIV_CLQs_REWvsFWHM_20191029.png}
   \vspace{-12pt}
  \caption[]{The Rest Equivalent Width (REW) vs. Full Width Half Maximum (FWHM) 
of the \civ\ emission line in the BOSS DR12 quasar sample using the catalogue 
of \citet{Hamann2017}. Note the REW logarithmic scaling.}
  \label{fig:REWvsFWHM}
\end{figure}

@@

\subsection{The Baldwin Effect}
The variable properties of the rest-frame UV quasar emission lines
have been long studied, with the global (or ensemble) Baldwin Effect
(the anti-correlation between the EW of the emission line and the
underlying continuum luminosity of single-epoch observations of a
large number of AGN, first noted in \citet{Baldwin1977}.  More
recently, the intrinsic Baldwin effect, the same anti-correlation but
in an individual, variable AGN.  The variable properties of high-$z$
quasars, however, has been less well studied. Reasons for this include
more massive systems will tend to have longer timescales e.g. with
$R_{\rm Sch}= 2GM /c^{2}$ and $t_{\rm dyn} =\sqrt{ R^{3}/GM}$ means
$t_{\rm dyn} \sim 6 G^{3} M^{3} / GM c^{2} \sim 6G^{2} M^{2} / c^{2}
$.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/CIV_CLQs_Baldwin_LBol_20191015.png}
   \vspace{-12pt}
   \caption[]{The Baldwin Plot. The bolometric luminosities are from \citet{Kozlowski2017},
     while the REW measurements are from \citet{Hamann2017}.}
  \label{fig:REWvsFWHM}
\end{figure}

@@

\noindent
We thank:
\begin{list}{$\circ$}{}  
  \item Andy Lawrence, Mike Hawkins and David Homan for useful discussion. 
\end{list}

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191031v3.tex
CIV tex/ tidy up

  \begin{tabu}{l ll  ll cc c r }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_REWvsFWHM_20191029.png}
   \vspace{-12pt}
  \caption[]{The Rest Equivalent Width (REW) vs. Full Width Half Maximum (FWHM) 
of the \civ\ emission line in the BOSS DR12 quasar sample using the catalogue 
of \citet{Hamann2017}. %Note the REW logarithmic scaling.
}
  \label{fig:REWvsFWHM}
\end{figure}

@@

\subsection{The Baldwin Effect}
The variable properties of the rest-frame UV quasar emission lines
have been long studied, with the global (or ensemble) Baldwin Effect
(the anti-correlation between the EW of the emission line and the
underlying continuum luminosity of single-epoch observations of a
large number of AGN, first noted in \citet{Baldwin1977}.  More
recently, the intrinsic Baldwin effect, the same anti-correlation but
in an individual, variable AGN.  The variable properties of high-$z$
quasars, however, has been less well studied. Reasons for this include
more massive systems will tend to have longer timescales with e.g.
$t_{\rm dyn}  \sim M^{2}$ if $t_{\rm dyn} = \sqrt{ R^{3}/GM}$ and $R_{\rm Sch}= 2GM /c^{2}$.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_Baldwin_20191104v3.png}
   \vspace{-12pt}
   \caption[]{The \civ\ Equivalent width and the underlying continuum luminosity,
     commonly referred to as The Baldwin Plot. The continuum luminosities are
     from \citet{Kozlowski2017},
     the REW measurements are Table~\ref{tab:Baldwin}.}
  \label{fig:CIV_Baldwin}
\end{figure}

@@

EHT2017 data includes tracks from four separate
days of observing,;each day is 2.8$r_{g}$ $c^{-1}$ \citep{EHT2019_PaperIV} timescale is short
compared to the decorrelation timescale of simulated images, which is
$\sim$50 $r_{g}$ $c^{-1}$, and smaller than the light-crossing time of the source
plasma.

From \citet{EHT2019_PaperI}, $M_{M87^{*}} = (6.5\pm0.7) \; \times \; 10^{9}$ $M_{\odot}$, 
\begin{equation}
R_{s} = 2 r_{g} =  2 GM/c^{2}  = 9.598 \times10^{12} {\rm m}.
\end{equation}
giving a {\it light crossing timescale} of $t_{\rm lt} = R_{s} / c = 32 015 {\rm secs}$ (0.37 days).
%\begin{equation}
%t_{\rm lt} = R_{s} / c = 32015 {\rm secs}$
%\end{equation}
%and a {\it dynamical timescale}, $t_{\rm dyn}$
%\begin{equation}
%$t_{\rm dyn}  =  sqrt{ R_{s}^{3}/G M}
% \end{equation}
%also (!!!!!) of $t_{\rm dyn}  =  \sqrt{ R_{s}^{3}/G M}$ = 32015 seconds.

>>>>

  \begin{tabu}{l ll  ll ccc c r }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/CIV_CLQs_REWvsFWHM_20191029.png}
   \vspace{-12pt}
  \caption[]{The Rest Equivalent Width (REW) vs. Full Width Half Maximum (FWHM) 
of the \civ\ emission line in the BOSS DR12 quasar sample using the catalogue 
of \citet{Hamann2017}. Note the REW logarithmic scaling.}
  \label{fig:REWvsFWHM}
\end{figure}

@@

\subsection{The Baldwin Effect}
The variable properties of the rest-frame UV quasar emission lines
have been long studied, with the global (or ensemble) Baldwin Effect
(the anti-correlation between the EW of the emission line and the
underlying continuum luminosity of single-epoch observations of a
large number of AGN, first noted in \citet{Baldwin1977}.  More
recently, the intrinsic Baldwin effect, the same anti-correlation but
in an individual, variable AGN.  The variable properties of high-$z$
quasars, however, has been less well studied. Reasons for this include
more massive systems will tend to have longer timescales with e.g.
$t_{\rm dyn} = \sqrt{ R^{3}/GM} \rightarrow  t_{\rm dyn}  \sim M^{2}$
if e.g. $R_{\rm Sch}= 2GM /c^{2}$.
%and $t_{\rm dyn} =\sqrt{ R^{3}/GM}$ means e.g $t_{\rm dyn} \sim 6 G^{3} M^{3} / GM c^{2} \sim 6G^{2} M^{2} / c^{2}.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/CIV_CLQs_Baldwin_LBol_20191015.png}
   \vspace{-12pt}
   \caption[]{The Baldwin Plot. The bolometric luminosities are from \citet{Kozlowski2017},
     while the REW measurements are from \citet{Hamann2017}.}
  \label{fig:CIV_Baldwin}
\end{figure}

@@

EHT2017 data includes tracks from four separate
days of observing,;each day is 2.8$r_{g}$ $c^{-1}$ \citep{(EHT_PaperIV} timescale is short
compared to the decorrelation timescale of simulated images, which is
$\sim$50 $r_{g}$ $c^{-1}$, and smaller than the light-crossing time of the source
plasma.

From \citet{EHT_PaperI}, $M_{M87^{*}} = (6.5\pm0.7) \; \times \; 10^{9}$ $M_{\odot}$, 
\begin{equation}
R_{s} = 2 r_{g} =  2 GM/c^{2}  = 9.598 \times10^{12} {\rm m}.
\end{equation}
giving a {\it light crossing timescale} of $t_{\rm lt} = R_{s} / c = 32 015 {\rm secs}$ (0.37 days).
%\begin{equation}
%t_{\rm lt} = R_{s} / c = 32015 {\rm secs}$
%\end{equation}
%and a {\it dynamical timescale}, $t_{\rm dyn}$
%\begin{equation}
%$t_{\rm dyn}  =  sqrt{ R_{s}^{3}/G M}
% \end{equation}
%also (!!!!!) of $t_{\rm dyn}  =  \sqrt{ R_{s}^{3}/G M}$ = 32015 seconds.
